### 2008-09-27 doc/client/arc-ws-clients.tex
Port number typo

The \verb:Chain: element, finally, defines how to combine the MCCs
that have been loaded into a communication chain. In this case, a TCP
MCC that connects to port 6000 on the local host is connected to a TLS
MCC, which is connected to a HTTP that uses the POST method, and
finally a SOAP MCC is connected to the HTTP MCC.

>>>>

The \verb:Chain: element, finally, defines how to combine the MCCs
that have been loaded into a communication chain. In this case, a TCP
MCC that connects to port 60000 on the local host is connected to a TLS
MCC, which is connected to a HTTP that uses the POST method, and
finally a SOAP MCC is connected to the HTTP MCC.
